---
title: "Lab 8"
author: "Samantha Kuglen"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data
```{r}
homes <- read_csv(here("data", "slo_homes.csv"))

#unique(homes$City) in console to get unique city names
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status)
- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status
```{r}
homes_sub  %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = round(mean(Price, na.rm = TRUE), 1),
            sd_price = round(sd(Price,na.rm = TRUE), 1))

# If you don't want to run this code at all: set eval = FALSE, code not evaluated
# if not referring to a variable, outside of aes
# higher density of homes sold towards lower prices at Santa Maria 
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + 
  scale_x_continuous(limits = c(0, 3e6))
```


Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and Point shape by sale status
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) + 
  geom_point(aes(color = City, shape = Status)) +
  geom_smooth(method = "lm") +
  theme_linedraw()
  
```
## Model the relationship with home price as DV
```{r}
# price per square foot and square foot redundant
# bed and bath correlated... square foot too... correlation about size of the house
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables, price, bed, bath, sqft
homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

# Interpretting varibales, reference level is City of Arroyo Grande, for 
# On average, Atascadero, house costs $9068 less than house in Arroyo Grande
# - $30792, for every additional bedroom, price decreases for each 1 additional bedroom that exists in the house
# Status: reference level is foreclosure, on average, regular sale has lower prices than those in foreclosure
# These don't make sense, redudant in model so reexamine model

# How would I explore diagnostic plots?
plot(homes_lm1)

```

Try another model where we simplify based on concerns:
- City 
- SqFt
- Status
```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

homes_lm2

plot(homes_lm2)
#use summary(homes_lm2) in the console to view coefficients

# these values more align with what you would expect for home prices, status regular price vs foreclosure price
# R^2 84% of the variance in home price is explained by the predictor variables in this model (city, sqft, status, pricepersqft, bedroom, bathroom)... other variables need to capture 100% of variance in price, 
# "adjusted" accounts for increased variables

# ideal model: has high fit and is simple... use AIC
```

Find the AIC value of each model, lower = better balance between model fit and complexity:
```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that might make sense, check out & compare model fit, outputs, and AIC value
```{r}
homes_lm3 <- lm(Price ~ City + SqFt + Status + Bedrooms, data = homes_sub)

plot(homes_lm3)
summary(homes_lm3)
AIC(homes_lm3)
```

Use `modelsummary` to show model outputs side-by-side:

If you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list.

```{r}
# comparison in table of models
# models 2 and 3 have lower R...capture less of the variance in price but not necessarily bad
# examine each variable to see what makes the most sense to describe what's going on
# in () in table... std error for each of the coefficients
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model
```{r}
#Use `broom::augment()`

homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create. 

# MY UPDATE ! ! ! !