---
title: "Lab 8"
author: "Samantha Kuglen"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data
```{r}
homes <- read_csv(here("data", "slo_homes.csv"))

#unique(homes$City) in console to get unique city names
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status)
- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status
```{r}
homes_sub  %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = round(mean(Price, na.rm = TRUE), 1),
            sd_price = round(sd(Price,na.rm = TRUE), 1))

# If you don't want to run this code at all: set eval = FALSE, code not evaluated
# if not referring to a variable, outside of aes
# higher density of homes sold towards lower prices at Santa Maria 
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + 
  scale_x_continuous(limits = c(0, 3e6))
```


Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and Point shape by sale status
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) + 
  geom_point(aes(color = City, shape = Status)) +
  geom_smooth(method = "lm") +
  theme_linedraw()
  
```


